A Switching Planner for Combined Task and Observation Planning

### 2010-11-30 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
last change fo the night

For the purposes of successive switching, execution of either a dual
action of the form $\assumptiveDT{i}$, or the
$\actions.\poss(\switchAction)$, returns control to a sequential
session. If a dual is executed, then the sequential planner must
replan with $\bstate_0$ equal to the underlying
belief-state. Otherwise, if $\actions.\poss(\switchAction)$ is
executed, then the current sequential plan is executed until further
sensing is scheduled, or to completion. Lastly, we note that in our
project the rewards, i.e., functions
$\$,\hat\$:2^\propositions\to\Re$, for the POMDP posed to the
contingent session are sourced from a motivational component of our
robotic architecture. For this paper, we set $\$(x)$ to be a positive
constant, and have $\hat\$(x)= - \$(x)(1 - p) / p$ where $p$ is the
probability that $x$ is true.

>>>>

For the purposes of successive switching, execution of either a dual
action of the form $\assumptiveDT{i}$, or the
$\actions.\poss(\switchAction)$, returns control to a sequential
session. If a dual is executed, then the sequential planner must
replan with $\bstate_0$ equal to the underlying
belief-state. Otherwise, if $\actions.\poss(\switchAction)$ is
executed, then the current sequential plan is executed until further
sensing is scheduled, or to completion. Lastly, we note that in our
project the rewards, i.e., functions
$\$,\hat\$:2^\propositions\to\Re$, for the POMDP posed to the
contingent session are sourced from a motivational component of our
robotic architecture. For this paper, for $\assumptiveDT{i}$ actions
we set $\$(x)$ to be a positive constant, and have $\hat\$(x)= -
\$(x)(1 - p) / p$ where $p$ is the probability that $x$ is true. For
$\actions.\poss(\switchAction)$ actions we have $\hat\$(x)= -
\$(x)p/(1-p)$.\footnote{These values were chosen to encourage sensing.}
